Growth and inequality in public good provision --- an extended replication

### 2022-11-05 analysis/quarto/paper.qmd
update paper

Today's actions are tomorrow's result. There are many settings in which current decisions affect future outcomes and with it, future decision spaces. Opting for environmental friendly policies today not only reduces carbon dioxide omissions but also helps us to reach the Paris climate targets tomorrow. Deferring these policies, the targets can be reached as well---but with less flexibility. Hence, today's actions (or the omission thereof) not only affect intermediate results but also the number of paths one can choose to reach certain goals.

Standard public good games---although often intended to inform climate policies^[See @GKLS2020 [p. 1] for numerous references.]---miss these temporal interdependencies because participants have the same set of actions in each period. A game implemented by Gächter, Mengel, Tsakas & Vostroknutov [-@GMTV2017] (hereafter, GMTV) as well as Stefan Große (2011, unpublished) incorporated interdependencies into a _dynamic_ public good game with students in Nottingham, England and Erfurt, Germany.

Because their setting is more realistic, one wonders whether it is better suited to inform public policy. To answer this question, I replicated parts of GMTV's experiment with different samples. In addition, I observed the participant's behavior in voluntary climate actions (VCA). This yielded a setting similar to @GKLS2020's which allows me to analyze how behavior in the abstract game translates into real-world action across samples.

I utilized an inexperienced sample that has not been exposed to interactive experiments before. Furthermore, I conducted the experiment online. This required me to make the experiment's software robust to minimize attrition. Because I observed metrics to assess the fluency and feasibility of online experiments, this study also serves as a case study like the one of @AGM2018.

@@

As in the NOPUNISH 10 Period treatment of GMTV, I ran sessions with groups of four ($i \in I=\{1,2,3,4\}$), an initial endowment of $N_i^1 = 20$ tokens^[A token was worth `r EXCHANGE_RATE` Euros.], $T=10$ periods, a private account with a return of $1$ and a group account with a return of $1.5$ ($\Rightarrow$ MPCR$\equiv \frac{1.5}{4}$), such that:

$$
N_i^{t+1}=N_i^t - c_i^t + \frac{1.5}{4}\sum_{j=1}^4 c_j^t
$$
What makes the game _dynamic_? Instead of receiving fresh endowments every period, participants received one endowment only at the beginning of the first period. A participant's endowment in the second period is the wealth he or she accumulated in the first period. A participant's endowment in the third period is the wealth he or she accumulated in the first two periods. And so on. Hence, a decision in one period has consequences on future endowments and, ultimately, growth paths. For this reason, the game is described as a _dynamic_ public good game

@@

Like GMTV we employ a real giving task after the abstract game. In contrast to GMTV and like @GKLS2020, we employed a VCA, where they could donate (some of) their earnings to offset carbon dioxide (that is, by retiring emission permits from the EU ETS).^[Importantly, @GKLS2020 made the VCA decision with a fresh endowment _before_ they played the abstract game. I deviate from their procedure to match GMTV's procedure.]
To ensure that each participant had the same basic level of information about the impact of their decision, I provided some basic information about the mechanism. The information also highlighted that the mitigation came into operation on a European level.
Finally, I informed the participants that the documentation of individual and aggregate contributions were posted immediately after the experiments online. To avoid privacy or social image concerns, participants learned their unique and random IDs, which they needed to identify their individual contributions.
This document certified that their contributions have been used to offset [1.82 tons](https://www.compensators.org/compensatelist/?searchterm=stefan+traub) of carbon dioxide emissions.

@@

I recruited the participants from the so called _[HamburgPanel](https://www.wiso.uni-hamburg.de/forschung/forschungslabor/umfragelabor/aktuelle-umfragen/hamburgpanel.html)_ using HROOT [@hroot]. The panel is provided by the University of Hamburg's Research Laboratory, which used a randomized last digits approach to build the panel while drawing from the population of citizens from Hamburg, Germany. Because the sample was exhausted at one point, I also recruited students from the University of Hamburg.

At the time I conducted the experiment, the representative sample was not familiar with interactive experiments. In fact, I ran the first interactive group experiment with this sample. The students, in contrast, are used to this kind of experiments. Recruiting them, I excluded those who have participated in a public goods game before. As a consequence, nonnaiveté is unlikely to affect the validity of my experiment [@GoodmanPaolacci2017 p. 204].

@@

The experiment was logistically complex for several reasons. First, the sample was inexperienced. Second, the experiment was interactive and synchronous. Third, the underlying game was dynamic and interdependent. This makes dropouts not only more likely, but also more expensive which is why dropouts were a major concern implementing the experiment.

I chose oTree [@oTree] to implement the experiment because it is open-source, well documented and very flexible. Its [Bootstrap](https://getbootstrap.com/) (a powerful frontend toolkit) integration allowed me to make the graphical user interface interactive, appealing and easy to navigate. The [Highcharts library](https://www.highcharts.com/) made it easy to visualize results and to communicate dynamics. The oTree code snippets made it possible to handle dropouts, for instance, by replacing them with artificial bots (and informing the rest of the group thereof). Insofar, oTree served a good tool to consider the participants' user experience and thus, to make dropouts less likely.

@@

The experiment lasted around `r total_completion_time` minutes on average. The earnings of the average subject were `r earningsMean %>% round(digits = 2)` Euros (sd = `r earningsSD  %>% round(digits = 2)`).^[This values include earnings from the incentivized risk elicitation task that are not part of the analysis.]

@@

Parts of the analyses are pre-registered [@preregistration]. In addition, I pre-registered the exact analyses I planned to run when I designed designed the experiment on [GitHub](https://github.com/Howquez/coopUncertainty/blob/July21Replication/analysis/reports/rmd).^[https://github.com/Howquez/coopUncertainty/tree/July21Replication/analysis/reports/rmd to run the code, you need to executed the .Rmd files in this repository in the order that is indicated by its file names.]. GitHub is a website and cloud-based service where developers---and researchers alike---can store and manage their code. The service is based on Git^[Git is a specific open-source version control system developed in 2005.] and designed for version control. Importantly, changes are timestamped and can be tracked. Moreover, one can create branches, that is, duplicates of code -- either to work collaborative or to archive a certain state. Accordingly, I archived my analyses scripts and created a [branch](https://github.com/Howquez/coopUncertainty/tree/July21Replication) a few days _before_ we collected data.

The analysis that makes the most sense now that you have collected the data is a little different, though: Because the more representative subject pool was exhausted earlier than expected, I recruited students unwantedly and changed parts of the scripts.^[The source code of this document contains the analysis and can be found [here](https://github.com/Howquez/coopUncertainty/blob/main/analysis/quarto/paper.qmd): https://github.com/Howquez/coopUncertainty/blob/main/analysis/quarto/paper.qmd] Because the originally planned analysis code is archived and reproducible, these changes are transparent.

@@

How did the participants, who have never participated in an online group experiment before, cope with the situation? Moreover, did participants understand the unfamiliar setting they found themselves in? While the answer to the former question requires more thought, the answer to the latter simply is _yes_: `r 67` out of `r 44 + 67 + 5` answered with _"yes"_ when I asked them. Another `r 44` answered with _"rather yes"_ while nobody indicated that he or she did not understand the situation at all. To analyze how participants coped with the situation, I consider three additional metrics: selection into the experiment,  attrition as well as the time spent on each page.

@@

**Result 3.** _Existing evidence overestimates the willingness to contribute to real public goods. This holds true for more representative samples and---to a lower degree---for student samples._

@@

The three most important findings are as follows: First, the contribution behavior in my experiment is statistically similar to the behavior reported in the original study. Consequently, the outcomes growth and inequality are similar as well. Second, the online experiment proceeded fluently such that dropouts were no concern. Third, contribution behavior in my abstract setting is, if anything, only weakly linked to behavior in the real world. This lack of generalizability can be counteracted, but not be solved, by the use of more representative samples.

The significance of the first result is that similar procedures led to replicable findings under different circumstances across two different samples. The second result is of methodological importance: It highlights that even logistically complex experiments can be conducted online with---not only with clickworkers but also with a true general population sample. The third result questions whether recruiting from more representative samples is worth the efforts because it decreases transferability of results to the real world---at least, a little.

>>>>

Today's actions are tomorrow's result. There are many settings in which current decisions affect future outcomes and with it, future decision spaces. Opting for environmental friendly policies today not only reduces carbon dioxide omissions immediately but also helps us to reach the Paris climate targets tomorrow. Deferring these policies, may not necessarily prevent us from reaching these targets, but it makes it more difficult in the future. Hence, today's actions (or the omission thereof) not only affect intermediate outcomes but also the number of paths one can choose to reach certain goals.

Standard public good games---although often intended to inform climate policies^[See @GKLS2020 [p. 1] for numerous references.]---miss these temporal interdependencies simply because participants have the same set of actions in each period. Accordingly, participants' actions in a given period do not affect their number of actions in subsequent periods. A game implemented by Gächter, Mengel, Tsakas & Vostroknutov [-@GMTV2017] (hereafter, GMTV) as well as Stefan Große (2011, unpublished) incorporated interdependencies into a _dynamic_ public good game. Here, participants' actions in a given period affect their number of actions in subsequent periods. Because there is surprisingly little experimental research on these interdependencies^[One exemption are @Moser2019, who built on GMTV's design do investigate leadership.], I replicated one of their treatments.

@GKLS2020 find that standard public good games do not generalize to real-world climate action. Because the dynamic setting has a more realistic property, one wonders whether it is better suited to inform public policy. To answer this question, I ran the experiment with different samples^[GMTV ran their experiments with students in Nottingham, England.] online, that is, with participants who make their decisions in an environment whcih is more natural than the lab. In addition, I observed the participants' behavior in voluntary climate actions (VCA). This yielded a setting similar to @GKLS2020's which allows me to analyze how behavior in the abstract game translates into real-world action across samples.

@AGM2018 conducted public good games in the lab and on MTurk to draw lessons from online experimentation. This study extends this literature [see also @GoodmanPaolacci2017] by focusing on a completely inexperienced sample that has not been exposed to interactive experiments before. This required me to design a robust (and thus, more complex) software to minimize attrition. In exchange, the online setting allowed me to also collect paradata to assess the fluency and feasibility of the experiment. This article reports on both topics: the robust design as well as the feasibility.

@@

As in the NOPUNISH 10 Period treatment of GMTV, I ran sessions with groups of four ($i \in I=\{1,2,3,4\}$), an initial endowment of $N_i^1 = 20$ tokens^[A token was worth `r EXCHANGE_RATE` Euros.], $T=10$ periods, a private account with a return of $1$ and a group account with a return of $1.5$ ($\Rightarrow$ MPCR$\equiv \frac{1.5}{4}$). With $i$'s contribution in period $t$ being $c_i^t$, the model looks as follows:

$$
N_i^{t+1}=N_i^t - c_i^t + \frac{1.5}{4}\sum_{j=1}^4 c_j^t
$$

What makes the game _dynamic_? Instead of receiving fresh endowments every period, participants received one endowment only at the beginning of the first period. A participant's endowment in the second period is the wealth he or she accumulated in the first period. A participant's endowment in the third period is the wealth he or she accumulated in the first two periods. And so on. Hence, a decision in one period has consequences on future endowments and, ultimately, growth paths. For this reason, the game is described as a _dynamic_ public good game

@@

Like GMTV we employ a real giving task after the abstract game. In contrast to GMTV and like @GKLS2020, we employed a VCA, where they could donate any amount their earnings to offset carbon dioxide (that is, retirine emission permits from the EU ETS).^[Importantly, @GKLS2020 made the VCA decision with a fresh endowment _before_ they played the abstract game. I deviate from their procedure to match GMTV's procedure.]
To ensure that each participant had the same basic level of information about the impact of their decision, I provided some basic information about the mechanism. The information also highlighted that the mitigation came into operation on a European level.
Finally, I informed the participants that the documentation of individual and aggregate contributions were to be posted immediately after the experiments online. To avoid privacy or social image concerns, participants learned their unique and random IDs, which they needed to identify their individual contributions.
The document certified that their contributions have been used to offset [1.82 tons](https://www.compensators.org/compensatelist/?searchterm=stefan+traub) of carbon dioxide emissions.

@@

I recruited the participants from the so called _[HamburgPanel](https://www.wiso.uni-hamburg.de/forschung/forschungslabor/umfragelabor/aktuelle-umfragen/hamburgpanel.html)_ using HROOT [@hroot]. The panel is provided by the University of Hamburg's Research Laboratory, which used a randomized last digits approach to build the panel while drawing from the population of citizens of Hamburg, Germany. Because the sample was exhausted at one point, I also recruited students from the University of Hamburg.

At the time I conducted the experiment, the more representative sample was not familiar with interactive experiments. In fact, I ran the first interactive group experiment with this sample. The students, in contrast, were used to this kind of experiments. Recruiting them, I excluded those who have participated in a public goods game before. As a consequence, nonnaiveté is unlikely to affect the validity of the experiment [@GoodmanPaolacci2017 p. 204].

@@

The experiment was logistically complex for several reasons. First, the sample was inexperienced. Second, the experiment was interactive and synchronous. Third, the underlying game was dynamic and interdependent. This makes dropouts not only more likely but also more expensive, which is why attrition was a major concern implementing the experiment.

I chose oTree [@oTree] to implement the experiment because it is open-source, well documented and very flexible. Its [Bootstrap](https://getbootstrap.com/) (a powerful frontend toolkit) integration allowed me to make the graphical user interface interactive, appealing and easy to navigate. The [Highcharts library](https://www.highcharts.com/) made it easy to visualize results and to communicate dynamics. Insofar, oTree served a good tool to enhance the participants' user experience and thus, to make dropouts less likely. Furthermore, the oTree code snippets made it possible to handle dropouts.

Which features were required to handle dropouts? First, participants had to be matched to form a group _after_ comprehension questions were answered successfully. Importantly, participants were grouped by the order they answered these questions to reduce waiting times. While waiting for other players to form the group, the participants saw a wait-page informing them that they are waiting for other participants to arrive and that they do not have to wait for longer than 10 minutes. The screen also informed them that they would receive a _patience bonus_ of one Euro after the expiration of that time (or what was left of it). Second, participants only had 10 minutes to make the first contribution and 4 minutes for the remaining contributions. After this time expired, participants were replaced by bots that made random contributions. In this case, the remaining group members were informed about the replacement. Both features were implemented to limit wait times and boredom for other participants. @sec-feasibility shows that the first feature became effective in some cases, wheres the second feature did not.

@@

The experiment lasted around `r total_completion_time` minutes on average. The earnings  averaged `r earningsMean %>% round(digits = 2)` Euros (sd = `r earningsSD  %>% round(digits = 2)`).^[This values include earnings from the incentivized risk elicitation task that is not part of the analysis.]

@@

Parts of the analyses were pre-registered in the American Economic Association's RCT Registry [@preregistration]. In addition, I pre-registered the exact analyses I planned to run when I designed designed the experiment on [GitHub](https://github.com/Howquez/coopUncertainty/blob/July21Replication/analysis/reports/rmd).^[https://github.com/Howquez/coopUncertainty/tree/July21Replication/analysis/reports/rmd to run the code, you need to executed the .Rmd files in this repository in the order that is indicated by its file names.]. GitHub is a website and cloud-based service where developers---and researchers alike---can store and manage their code. The service is based on Git^[Git is a specific open-source version control system developed in 2005.] and designed for version control. Importantly, changes are timestamped and can be tracked. Moreover, one can create branches, that is, duplicates of code -- either to work collaborative or to archive a certain state. Accordingly, I archived my analyses scripts and created a [branch](https://github.com/Howquez/coopUncertainty/tree/July21Replication) a few days _before_ we collected data.

The analysis that makes the most sense now that I have collected the data is a little different though: Because the more representative subject pool was exhausted earlier than expected, I recruited students unwantedly and changed parts of the scripts.^[The source code of this document contains the analysis and can be found [here](https://github.com/Howquez/coopUncertainty/blob/main/analysis/quarto/paper.qmd): https://github.com/Howquez/coopUncertainty/blob/main/analysis/quarto/paper.qmd] However, because the originally planned analysis code is archived and reproducible, these changes are transparent and easy to assess.

@@

```{r reviewInformation}
#| eval: false

# to see how many people clicked on the popups to review instructions: 
full[dPGG.1.player.review_instructions !=0, .N]
full[dPGG.2.player.review_instructions !=0, .N]
#...

# or for contact information
full[dPGG.1.player.review_contact !=0, .N]
full[dPGG.2.player.review_contact !=0, .N]
# ...

How did the participants, who have never participated in an online group experiment before, cope with the situation? Moreover, did participants understand the unfamiliar setting they found themselves in? While the answer to the former question requires more thought, the answer to the latter simply is _yes_: `r 67` out of `r 44 + 67 + 5` answered with _"yes"_ when I asked them. Another `r 44` answered with _"rather yes"_ while nobody indicated that he or she did not understand the situation at all. There is some behavioral data supporting this finding: The user interface offered a popup to review instructions or contact information. I tracked both and find that none of the participants ever opened these popups even though they were clearly visible in the decision screen's header and introduced in the instructions. To  further analyze how participants coped with the situation, I consider three additional metrics: selection into the experiment, attrition as well as the time spent on each page.

@@

**Result 3.** _Overall, contribution behavior is uncorrelated with the willingness to contribute to real public goods. This holds true for more representative samples and---to a lower degree---for student samples._

@@

The three most important findings are as follows: First, the contribution behavior in my experiment is statistically similar to the behavior reported in the original study. Consequently, the outcomes growth and inequality are similar as well. Second, the online experiment proceeded fluently such that dropouts were no concern. Third, contribution behavior in my abstract setting is, if anything, only weakly linked to behavior in the real world.

The significance of the first result is that similar procedures led to replicable findings under different circumstances across two different samples. The second result is of methodological importance: It highlights that even logistically complex experiments can be conducted online with---not only with clickworkers but also with a true general population sample. The third result questions whether recruiting from more representative samples is worth the efforts because it decreases transferability of results to the real world---at least in this specific case.

### 2022-11-05 analysis/quarto/paper.tex
update paper

\begin{keyword}
    Replication study \sep Non-convenience sample \sep Open
science \sep Dynamic public good game \sep Online experiment \sep 
    Generalizability
\end{keyword}
\end{frontmatter}\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[interior hidden, frame hidden, sharp corners, enhanced, breakable, boxrule=0pt, borderline west={3pt}{0pt}{shadecolor}]}{\end{tcolorbox}}\fi

@@

Today's actions are tomorrow's result. There are many settings in which
current decisions affect future outcomes and with it, future decision
spaces. Opting for environmental friendly policies today not only
reduces carbon dioxide omissions but also helps us to reach the Paris
climate targets tomorrow. Deferring these policies, the targets can be
reached as well---but with less flexibility. Hence, today's actions (or
the omission thereof) not only affect intermediate results but also the
number of paths one can choose to reach certain goals.

Standard public good games---although often intended to inform climate
policies\footnote{See \citet[p.~1]{GKLS2020} for numerous references.}---miss
these temporal interdependencies because participants have the same set
of actions in each period. A game implemented by Gächter, Mengel, Tsakas
\& Vostroknutov \citeyearpar{GMTV2017} (hereafter, GMTV) as well as
Stefan Große (2011, unpublished) incorporated interdependencies into a
\emph{dynamic} public good game with students in Nottingham, England and
Erfurt, Germany.

Because their setting is more realistic, one wonders whether it is
better suited to inform public policy. To answer this question, I
replicated parts of GMTV's experiment with different samples. In
addition, I observed the participant's behavior in voluntary climate
actions (VCA). This yielded a setting similar to \citet{GKLS2020}'s
which allows me to analyze how behavior in the abstract game translates
into real-world action across samples.

I utilized an inexperienced sample that has not been exposed to
interactive experiments before. Furthermore, I conducted the experiment
online. This required me to make the experiment's software robust to
minimize attrition. Because I observed metrics to assess the fluency and
feasibility of online experiments, this study also serves as a case
study like the one of \citet{AGM2018}.

@@

As in the NOPUNISH 10 Period treatment of GMTV, I ran sessions with
groups of four (\(i \in I=\{1,2,3,4\}\)), an initial endowment of
\(N_i^1 = 20\) tokens\footnote{A token was worth 0.05 Euros.}, \(T=10\)
periods, a private account with a return of \(1\) and a group account
with a return of \(1.5\) (\(\Rightarrow\) MPCR\(\equiv \frac{1.5}{4}\)),
such that:

\[
N_i^{t+1}=N_i^t - c_i^t + \frac{1.5}{4}\sum_{j=1}^4 c_j^t
\] What makes the game \emph{dynamic}? Instead of receiving fresh
endowments every period, participants received one endowment only at the
beginning of the first period. A participant's endowment in the second
period is the wealth he or she accumulated in the first period. A
participant's endowment in the third period is the wealth he or she
accumulated in the first two periods. And so on. Hence, a decision in
one period has consequences on future endowments and, ultimately, growth
paths. For this reason, the game is described as a \emph{dynamic} public
good game

@@

Like GMTV we employ a real giving task after the abstract game. In
contrast to GMTV and like \citet{GKLS2020}, we employed a VCA, where
they could donate (some of) their earnings to offset carbon dioxide
(that is, by retiring emission permits from the EU ETS).\footnote{Importantly,
  \citet{GKLS2020} made the VCA decision with a fresh endowment
  \emph{before} they played the abstract game. I deviate from their
  procedure to match GMTV's procedure.} To ensure that each participant
had the same basic level of information about the impact of their
decision, I provided some basic information about the mechanism. The
information also highlighted that the mitigation came into operation on
a European level. Finally, I informed the participants that the
documentation of individual and aggregate contributions were posted
immediately after the experiments online. To avoid privacy or social
image concerns, participants learned their unique and random IDs, which
they needed to identify their individual contributions. This document
certified that their contributions have been used to offset
\href{https://www.compensators.org/compensatelist/?searchterm=stefan+traub}{1.82
tons} of carbon dioxide emissions.

@@

I recruited the participants from the so called
\emph{\href{https://www.wiso.uni-hamburg.de/forschung/forschungslabor/umfragelabor/aktuelle-umfragen/hamburgpanel.html}{HamburgPanel}}
using HROOT \citep{hroot}. The panel is provided by the University of
Hamburg's Research Laboratory, which used a randomized last digits
approach to build the panel while drawing from the population of
citizens from Hamburg, Germany. Because the sample was exhausted at one
point, I also recruited students from the University of Hamburg.

At the time I conducted the experiment, the representative sample was
not familiar with interactive experiments. In fact, I ran the first
interactive group experiment with this sample. The students, in
contrast, are used to this kind of experiments. Recruiting them, I
excluded those who have participated in a public goods game before. As a
consequence, nonnaiveté is unlikely to affect the validity of my
experiment \citep[ p.~204]{GoodmanPaolacci2017}.

@@

The experiment was logistically complex for several reasons. First, the
sample was inexperienced. Second, the experiment was interactive and
synchronous. Third, the underlying game was dynamic and interdependent.
This makes dropouts not only more likely, but also more expensive which
is why dropouts were a major concern implementing the experiment.

I chose oTree \citep{oTree} to implement the experiment because it is
open-source, well documented and very flexible. Its
\href{https://getbootstrap.com/}{Bootstrap} (a powerful frontend
toolkit) integration allowed me to make the graphical user interface
interactive, appealing and easy to navigate. The
\href{https://www.highcharts.com/}{Highcharts library} made it easy to
visualize results and to communicate dynamics. The oTree code snippets
made it possible to handle dropouts, for instance, by replacing them
with artificial bots (and informing the rest of the group thereof).
Insofar, oTree served a good tool to consider the participants' user
experience and thus, to make dropouts less likely.

@@

The experiment lasted around 25 minutes on average. The earnings of the
average subject were 11.23 Euros (sd = 4.85).\footnote{This values
  include earnings from the incentivized risk elicitation task that are
  not part of the analysis.}

@@

Parts of the analyses are pre-registered \citep{preregistration}. In
addition, I pre-registered the exact analyses I planned to run when I
designed designed the experiment on
\href{https://github.com/Howquez/coopUncertainty/blob/July21Replication/analysis/reports/rmd}{GitHub}.\footnote{https://github.com/Howquez/coopUncertainty/tree/July21Replication/analysis/reports/rmd
  to run the code, you need to executed the .Rmd files in this
  repository in the order that is indicated by its file names.}. GitHub
is a website and cloud-based service where developers---and researchers
alike---can store and manage their code. The service is based on
Git\footnote{Git is a specific open-source version control system
  developed in 2005.} and designed for version control. Importantly,
changes are timestamped and can be tracked. Moreover, one can create
branches, that is, duplicates of code -- either to work collaborative or
to archive a certain state. Accordingly, I archived my analyses scripts
and created a
\href{https://github.com/Howquez/coopUncertainty/tree/July21Replication}{branch}
a few days \emph{before} we collected data.

The analysis that makes the most sense now that you have collected the
data is a little different, though: Because the more representative
subject pool was exhausted earlier than expected, I recruited students
unwantedly and changed parts of the scripts.\footnote{The source code of
  this document contains the analysis and can be found
  \href{https://github.com/Howquez/coopUncertainty/blob/main/analysis/quarto/paper.qmd}{here}:
  https://github.com/Howquez/coopUncertainty/blob/main/analysis/quarto/paper.qmd}
Because the originally planned analysis code is archived and
reproducible, these changes are transparent.

@@

How did the participants, who have never participated in an online group
experiment before, cope with the situation? Moreover, did participants
understand the unfamiliar setting they found themselves in? While the
answer to the former question requires more thought, the answer to the
latter simply is \emph{yes}: 67 out of 116 answered with \emph{``yes''}
when I asked them. Another 44 answered with \emph{``rather yes''} while
nobody indicated that he or she did not understand the situation at all.
To analyze how participants coped with the situation, I consider three
additional metrics: selection into the experiment, attrition as well as
the time spent on each page.

@@

\textbf{Result 3.} \emph{Existing evidence overestimates the willingness
to contribute to real public goods. This holds true for more
representative samples and---to a lower degree---for student samples.}

>>>>

\begin{keyword}
    Replication study \sep Non-convenience sample \sep Open
science \sep Dynamic public good game \sep Online experiment \sep 
    Generalizability
\end{keyword}
\end{frontmatter}\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[enhanced, frame hidden, interior hidden, boxrule=0pt, borderline west={3pt}{0pt}{shadecolor}, sharp corners, breakable]}{\end{tcolorbox}}\fi

@@

Today's actions are tomorrow's result. There are many settings in which
current decisions affect future outcomes and with it, future decision
spaces. Opting for environmental friendly policies today not only
reduces carbon dioxide omissions immediately but also helps us to reach
the Paris climate targets tomorrow. Deferring these policies, may not
necessarily prevent us from reaching these targets, but it makes it more
difficult in the future. Hence, today's actions (or the omission
thereof) not only affect intermediate outcomes but also the number of
paths one can choose to reach certain goals.

Standard public good games---although often intended to inform climate
policies\footnote{See \citet[p.~1]{GKLS2020} for numerous references.}---miss
these temporal interdependencies simply because participants have the
same set of actions in each period. Accordingly, participants' actions
in a given period do not affect their number of actions in subsequent
periods. A game implemented by Gächter, Mengel, Tsakas \& Vostroknutov
\citeyearpar{GMTV2017} (hereafter, GMTV) as well as Stefan Große (2011,
unpublished) incorporated interdependencies into a \emph{dynamic} public
good game. Here, participants' actions in a given period affect their
number of actions in subsequent periods. Because there is surprisingly
little experimental research on these interdependencies\footnote{One
  exemption are \citet{Moser2019}, who built on GMTV's design do
  investigate leadership.}, I replicated one of their treatments.

\citet{GKLS2020} find that standard public good games do not generalize
to real-world climate action. Because the dynamic setting has a more
realistic property, one wonders whether it is better suited to inform
public policy. To answer this question, I ran the experiment with
different samples\footnote{GMTV ran their experiments with students in
  Nottingham, England.} online, that is, with participants who make
their decisions in an environment whcih is more natural than the lab. In
addition, I observed the participants' behavior in voluntary climate
actions (VCA). This yielded a setting similar to \citet{GKLS2020}'s
which allows me to analyze how behavior in the abstract game translates
into real-world action across samples.

\citet{AGM2018} conducted public good games in the lab and on MTurk to
draw lessons from online experimentation. This study extends this
literature \citep[see also][]{GoodmanPaolacci2017} by focusing on a
completely inexperienced sample that has not been exposed to interactive
experiments before. This required me to design a robust (and thus, more
complex) software to minimize attrition. In exchange, the online setting
allowed me to also collect paradata to assess the fluency and
feasibility of the experiment. This article reports on both topics: the
robust design as well as the feasibility.

@@

As in the NOPUNISH 10 Period treatment of GMTV, I ran sessions with
groups of four (\(i \in I=\{1,2,3,4\}\)), an initial endowment of
\(N_i^1 = 20\) tokens\footnote{A token was worth 0.05 Euros.}, \(T=10\)
periods, a private account with a return of \(1\) and a group account
with a return of \(1.5\) (\(\Rightarrow\) MPCR\(\equiv \frac{1.5}{4}\)).
With \(i\)'s contribution in period \(t\) being \(c_i^t\), the model
looks as follows:

\[
N_i^{t+1}=N_i^t - c_i^t + \frac{1.5}{4}\sum_{j=1}^4 c_j^t
\]

What makes the game \emph{dynamic}? Instead of receiving fresh
endowments every period, participants received one endowment only at the
beginning of the first period. A participant's endowment in the second
period is the wealth he or she accumulated in the first period. A
participant's endowment in the third period is the wealth he or she
accumulated in the first two periods. And so on. Hence, a decision in
one period has consequences on future endowments and, ultimately, growth
paths. For this reason, the game is described as a \emph{dynamic} public
good game

@@

Like GMTV we employ a real giving task after the abstract game. In
contrast to GMTV and like \citet{GKLS2020}, we employed a VCA, where
they could donate any amount their earnings to offset carbon dioxide
(that is, retirine emission permits from the EU ETS).\footnote{Importantly,
  \citet{GKLS2020} made the VCA decision with a fresh endowment
  \emph{before} they played the abstract game. I deviate from their
  procedure to match GMTV's procedure.} To ensure that each participant
had the same basic level of information about the impact of their
decision, I provided some basic information about the mechanism. The
information also highlighted that the mitigation came into operation on
a European level. Finally, I informed the participants that the
documentation of individual and aggregate contributions were to be
posted immediately after the experiments online. To avoid privacy or
social image concerns, participants learned their unique and random IDs,
which they needed to identify their individual contributions. The
document certified that their contributions have been used to offset
\href{https://www.compensators.org/compensatelist/?searchterm=stefan+traub}{1.82
tons} of carbon dioxide emissions.

@@

I recruited the participants from the so called
\emph{\href{https://www.wiso.uni-hamburg.de/forschung/forschungslabor/umfragelabor/aktuelle-umfragen/hamburgpanel.html}{HamburgPanel}}
using HROOT \citep{hroot}. The panel is provided by the University of
Hamburg's Research Laboratory, which used a randomized last digits
approach to build the panel while drawing from the population of
citizens of Hamburg, Germany. Because the sample was exhausted at one
point, I also recruited students from the University of Hamburg.

At the time I conducted the experiment, the more representative sample
was not familiar with interactive experiments. In fact, I ran the first
interactive group experiment with this sample. The students, in
contrast, were used to this kind of experiments. Recruiting them, I
excluded those who have participated in a public goods game before. As a
consequence, nonnaiveté is unlikely to affect the validity of the
experiment \citep[ p.~204]{GoodmanPaolacci2017}.

@@

The experiment was logistically complex for several reasons. First, the
sample was inexperienced. Second, the experiment was interactive and
synchronous. Third, the underlying game was dynamic and interdependent.
This makes dropouts not only more likely but also more expensive, which
is why attrition was a major concern implementing the experiment.

I chose oTree \citep{oTree} to implement the experiment because it is
open-source, well documented and very flexible. Its
\href{https://getbootstrap.com/}{Bootstrap} (a powerful frontend
toolkit) integration allowed me to make the graphical user interface
interactive, appealing and easy to navigate. The
\href{https://www.highcharts.com/}{Highcharts library} made it easy to
visualize results and to communicate dynamics. Insofar, oTree served a
good tool to enhance the participants' user experience and thus, to make
dropouts less likely. Furthermore, the oTree code snippets made it
possible to handle dropouts.

Which features were required to handle dropouts? First, participants had
to be matched to form a group \emph{after} comprehension questions were
answered successfully. Importantly, participants were grouped by the
order they answered these questions to reduce waiting times. While
waiting for other players to form the group, the participants saw a
wait-page informing them that they are waiting for other participants to
arrive and that they do not have to wait for longer than 10 minutes. The
screen also informed them that they would receive a \emph{patience
bonus} of one Euro after the expiration of that time (or what was left
of it). Second, participants only had 10 minutes to make the first
contribution and 4 minutes for the remaining contributions. After this
time expired, participants were replaced by bots that made random
contributions. In this case, the remaining group members were informed
about the replacement. Both features were implemented to limit wait
times and boredom for other participants. Section~\ref{sec-feasibility}
shows that the first feature became effective in some cases, wheres the
second feature did not.

@@

The experiment lasted around 25 minutes on average. The earnings
averaged 11.23 Euros (sd = 4.85).\footnote{This values include earnings
  from the incentivized risk elicitation task that is not part of the
  analysis.}

@@

Parts of the analyses were pre-registered in the American Economic
Association's RCT Registry \citep{preregistration}. In addition, I
pre-registered the exact analyses I planned to run when I designed
designed the experiment on
\href{https://github.com/Howquez/coopUncertainty/blob/July21Replication/analysis/reports/rmd}{GitHub}.\footnote{https://github.com/Howquez/coopUncertainty/tree/July21Replication/analysis/reports/rmd
  to run the code, you need to executed the .Rmd files in this
  repository in the order that is indicated by its file names.}. GitHub
is a website and cloud-based service where developers---and researchers
alike---can store and manage their code. The service is based on
Git\footnote{Git is a specific open-source version control system
  developed in 2005.} and designed for version control. Importantly,
changes are timestamped and can be tracked. Moreover, one can create
branches, that is, duplicates of code -- either to work collaborative or
to archive a certain state. Accordingly, I archived my analyses scripts
and created a
\href{https://github.com/Howquez/coopUncertainty/tree/July21Replication}{branch}
a few days \emph{before} we collected data.

The analysis that makes the most sense now that I have collected the
data is a little different though: Because the more representative
subject pool was exhausted earlier than expected, I recruited students
unwantedly and changed parts of the scripts.\footnote{The source code of
  this document contains the analysis and can be found
  \href{https://github.com/Howquez/coopUncertainty/blob/main/analysis/quarto/paper.qmd}{here}:
  https://github.com/Howquez/coopUncertainty/blob/main/analysis/quarto/paper.qmd}
However, because the originally planned analysis code is archived and
reproducible, these changes are transparent and easy to assess.

@@

How did the participants, who have never participated in an online group
experiment before, cope with the situation? Moreover, did participants
understand the unfamiliar setting they found themselves in? While the
answer to the former question requires more thought, the answer to the
latter simply is \emph{yes}: 67 out of 116 answered with \emph{``yes''}
when I asked them. Another 44 answered with \emph{``rather yes''} while
nobody indicated that he or she did not understand the situation at all.
There is some behavioral data supporting this finding: The user
interface offered a popup to review instructions or contact information.
I tracked both and find that none of the participants ever opened these
popups even though they were clearly visible in the decision screen's
header and introduced in the instructions. To further analyze how
participants coped with the situation, I consider three additional
metrics: selection into the experiment, attrition as well as the time
spent on each page.

@@

\textbf{Result 3.} \emph{Overall, contribution behavior is uncorrelated
with the willingness to contribute to real public goods. This holds true
for more representative samples and---to a lower degree---for student
samples.}
